|

### 2024-06-23 README.qmd
changes

## Example

@@

## Bin data into suitable length categories for plotting

@@

(p <- ggplot()  + 
  geom_point(data = data_binned, aes(x = x_bin, y = p), col = "black") + 
  ylim(0, 1) +
  labs(x = "Fork length (cm)", y = "Proportion in maternal condition"))
```

>>>>

# Example

## Load data

@@

Bin data into suitable length categories for plotting.

@@

ggplot()  + 
  geom_point(data = data_binned, aes(x = x_bin, y = p), col = "black") + 
  ylim(0, 1) +
  labs(x = "Fork length (cm)", y = "Proportion in maternal condition")
```

Add marginal rug plots to show individual data points.

```{r}
ggplot()  + 
  geom_rug(data = filter(data, z == 1), aes(x = x), sides = "t") +
  geom_rug(data = filter(data, z == 0), aes(x = x), sides = "b") +
  geom_point(data = data_binned, aes(x = x_bin, y = p), col = "black") + 
  ylim(0, 1) +
  labs(x = "Fork length (cm)", y = "Proportion in maternal condition")

## Run model

### 2024-06-23 reports/revision/main-text.tex
changes

For the live-bearing and egg-laying class of chondrichthyan fishes a three parameter logistic `maternity' function with a variable upper asymptote, \(P_{Max}\), can be used to predict the average probability of a female giving birth or laying eggs in a season. Although fundamental to calculating the reproductive capacity of a population, few studies report maternity functions, with maturity functions often used as a proxy. Applying logistic models to simulated and empirical data showed that it was feasible to estimate \(P_{Max}\) from maternal data and that accuracy, bias, and confidence interval coverage often improved compared to when a fixed value was used. However, sample sizes of 100 - 200 maternal females were required for accurate estimation of \(P_{Max}\). Maturity parameters could be estimated with greater accuracy; however, substituting them for maternity parameters overestimated lifetime reproductive output. Greater use of maternity functions has the potential to improve calculation of reproductive output in quantitative populations models. In addition to improvements in parameter estimation, this method involves fewer assumptions and enables statistical inferences to be made on frequency of reproduction.

@@

When using the 3PLF methods model performance typically declined as the periodicity of the reproductive cycle increased. This is seen in the positive correlation between \(\hat{L'_{50}}\) and \(\hat{P_{Max}}\), whereby true underlying \(P_{Max}\) affected the magnitude and direction of bias in these parameters (Figure 2). With lower values of \(P_{Max}\) it appeared to be more difficult for the model to separate the point of inflection in the logistic model and the upper asymptote. As true underlying \(P_{Max}\) decreased there was also a greater potential for positive bias in \(\hat{P_{Max}}\). Additionally, longer reproductive cycles resulted in fewer maternal females, which was associated with larger bias (Figure 2).

@@

The effect of the different methods in ultimately calculating \(R_0\) varied considerably across the various scenarios. For school sharks, estimating \(P_{Max}\), was the most effective way to minimize bias in most scenarios (Figure S10). Substituting maturity parameters (2PLF-maturity method) led to a median overestimation of \(R_0\) by 3.4\% across all scenarios, while the 2PLF-maternity method led to a median underestimate of 11.1\%. (Figure S10). In contrast, for the gummy shark substituting maturity parameters led to a median overestimation of \(R_0\) of just 1\% across all scenarios which outperformed the 3PLF methods in several instances (Figure S11). Using the 2PLF method for gummy sharks led to a median overestimate of \(R_0\) of 22\% (Figure S10). For both species, better accuracy in calculating \(R_0\) was achieved with the 3PLF methods, with the 3PLF-estimated method performing best in most scenarios tested (Figure 6, Figure S12). For gummy sharks the 3PLF-fixed method performed best at lower sample sizes and lower values of \(P_{Max}\).

@@

Relatively few reproductive biology studies have used maternity functions to model maternal reproductive output in chondrichthyan fishes. Where they have been employed the approach has typically been to use a three parameter logistic function with a fixed, user-defined value for the upper asymptote, \(P_{Max}\). Here we show that it is feasible to estimate \(P_{Max}\) from maternal data, in turn enabling statistical inferences on reproductive periodicity. Applying 3PLF models with estimated and fixed values of \(P_{Max}\) to simulated data showed that accuracy, bias, and confidence interval coverage often improved when \(P_{Max}\) was estimated. Using a fixed value for \(P_{Max}\) in some cases reduced bias. Overall, however, relatively large sample sizes were needed to accurately estimate \(P_{Max}\), particularly with longer reproductive cycles. This study also demonstrated that, in some cases, recruitment can be overestimated when maturity data were used to approximate maternal data and inaccurate if \(P_{Max}\) was ignored when estimating maternity parameters. Based on these findings we outline considerations for practitioners using these methods and illustrate how they can provide novel insights into reproductive biology. We conclude by discussing the advantages of adopting this approach and future directions.

@@

Using simulated data to compare the relative performance of the 3PLF-estimated and 3PLF-fixed methods subject to a range of variables showed that it was feasible to estimate \(P_{Max}\), but was difficult to do so accurately. For non-annual reproductive cycles, \(> 100\) school sharks and \(> 200\) gummy sharks in maternal condition were typically needed to estimate \(P_{Max}\) with \textless10\% MARE (Figure 5). This indicates that the both sample size requirements and levels of uncertainty are likely to be larger than conventional logistic maturity analysis (Roa et al. 1999). In the case of the gummy shark this inaccuracy led to the 2PLF-maturity method performing comparably or better than the 3PLF methods in minimizing bias in \(R_0\) (Figure S11) Relatively wide confidence intervals were also obtained for \(P_{Max}\) in the empirical analysis for sandbar sharks, even with a total sample size of \textgreater{} 1000 females, of which 206 were in maternal condition. A similar sample size was used by Colonello \emph{et al}. (2016) to estimate plausible values of \(P_{Max}\) and maternity parameters for south Atlantic spiny dogfish.

@@

This unexpected result may be related to the gradual attainment of asymptotic maternal status. Maturity in sandbar sharks appears to occur over an extended size range. \(L_{5}\) and \(L_{95}\) are 146cm and 176cm -- a length interval that corresponds to around seven years given the sandbar shark's slow growth rate (Hale and Baremore 2013). With females maturing over a broad range of sizes and ages, it is possible that smaller females reproduce less frequently. The outcomes of this study suggest that larger sharks may ultimately be capable of reproducing biennially. Given that few females appear to attain this size (Hale and Baremore 2013). this suggests the modal reproductive frequency likely still at least triennial. Further work would be required to confirm this hypothesis, however, such an outcome would have important implications for management; not only are larger females more fecund (Baremore and Hale 2012), they also reproduce more frequently. This implies that size selective fishing or the removal of larger and older female sharks could have a disproportionately greater impact on population productivity.

@@

Estimation of \(P_{Max}\) using the 3PLF-estimated method may also be a means to resolving the longstanding question of reproductive frequency in some rare and threatened chondrichthyans. White sharks, \emph{Carcharodon carcharias}, and whale shark, \emph{Rhinchodon typus}, are two examples of intensively studied species where only fragmentary observations of female reproductive biology exist (Joung et al. 1996, Sato et al. 2016). In both species lack of data on reproductive frequency is a major impediment to population modelling and the development of management strategies (Huveneers et al. 2018, Bowlby and Gibson 2020). With many of these populations the focus of ongoing monitoring, non-lethal methods for assessing maternal state may eventually provide a way of collecting sufficient data for estimation of \(P_{Max}\) (Sulikowski et al. 2016).

@@

\bibitem[\citeproctext]{ref-natanson_presence_2019}
Natanson, L.J., Deacy, B.M., Joyce, W., and Sulikowski, J. 2019. Presence of a resting population of female porbeagles ({Lamna} nasus), indicating a biennial reproductive cycle, in the western {North} {Atlantic} {Ocean}. Fish. B-noaa. \textbf{117}.

>>>>

For the live-bearing and egg-laying class of chondrichthyan fishes a three parameter logistic `maternity' function with a variable upper asymptote, \(P_{Max}\), can be used to predict the average probability of a female giving birth or laying eggs in a season. Although fundamental to calculating the reproductive capacity of a population, few studies report maternity functions, with maturity functions often used as a proxy. Applying logistic models to simulated and empirical data showed that it was feasible to estimate \(P_{Max}\) from maternal data and that accuracy, bias, and confidence interval coverage often improved compared to when a fixed value was used. However, sample sizes of 100 - 200 maternal females were typically required for accurate estimation of \(P_{Max}\). While maturity parameters could be estimated with greater accuracy, substituting them for maternity parameters overestimated lifetime reproductive output. Greater use of maternity functions has the potential to improve calculation of reproductive output in quantitative populations models. In addition to improvements in parameter estimation, this method involves fewer assumptions and enables statistical inferences to be made on frequency of reproduction.

@@

When using the 3PLF methods model performance typically declined as the periodicity of the reproductive cycle increased. This is seen in the positive correlation between \(\hat{L'_{50}}\) and \(\hat{P_{Max}}\), whereby true underlying \(P_{Max}\) affected the magnitude and direction of bias in these parameters (Figure 2). With lower values of \(P_{Max}\) it appeared to be more difficult for the model to separate the point of inflection in the logistic model and the upper asymptote. As true underlying \(P_{Max}\) decreased there was also a greater potential for positive bias in \(\hat{P_{Max}}\). Additionally, longer reproductive cycles resulted in fewer females in maternal condition, which was associated with larger bias (Figure 2).

@@

The effect of the different methods in ultimately calculating \(R_0\) varied considerably across the various scenarios. For school sharks, estimating \(P_{Max}\), was the most effective way to minimize bias in most scenarios (Figure S10). Substituting maturity parameters (2PLF-maturity method) led to a median overestimation of \(R_0\) by 3.4\% across all scenarios, while the 2PLF-maternity method led to a median underestimate of 11.1\%. (Figure S10). In contrast, for the gummy shark substituting maturity parameters led to a median overestimation of \(R_0\) of just 1\% across all scenarios which outperformed the 3PLF methods in many instances (Figure S11). Using the 2PLF method for gummy sharks led to a median overestimate of \(R_0\) of 22\% (Figure S10). For both species, better accuracy in calculating \(R_0\) was achieved with the 3PLF methods, with the 3PLF-estimated method performing best in most scenarios tested (Figure 6, Figure S12). For gummy sharks the 3PLF-fixed method performed best at lower sample sizes and lower values of \(P_{Max}\).

@@

Relatively few reproductive biology studies have used maternity functions to model maternal reproductive output in chondrichthyan fishes. Where they have been employed the approach has typically been to use a three parameter logistic function with a fixed, user-defined value for the upper asymptote, \(P_{Max}\). Here we show that it is feasible to estimate \(P_{Max}\) from maternal data, in turn enabling statistical inferences on reproductive periodicity. Applying 3PLF models with estimated and fixed values of \(P_{Max}\) to simulated data showed that accuracy, bias, and confidence interval coverage often improved when \(P_{Max}\) was estimated. Using a fixed value for \(P_{Max}\) in some cases reduced bias. Overall, however, relatively large sample sizes were needed to accurately estimate \(P_{Max}\), particularly with longer reproductive cycles. This study also demonstrated that, in some cases, recruitment was overestimated when maturity data were used to approximate maternal data and inaccurate if \(P_{Max}\) was ignored when estimating maternity parameters. Based on these findings we outline considerations for practitioners using these methods and illustrate how they can provide novel insights into reproductive biology. We conclude by discussing the advantages of adopting this approach and future directions.

@@

Using simulated data to compare the relative performance of the 3PLF-estimated and 3PLF-fixed methods subject to a range of variables showed that it was feasible to estimate \(P_{Max}\), but was difficult to do so accurately. For non-annual reproductive cycles, \(> 100\) school sharks and \(> 200\) gummy sharks in maternal condition were typically needed to estimate \(P_{Max}\) with \textless10\% MARE (Figure 5). This indicates that the both sample size requirements and levels of uncertainty are likely to be larger than conventional logistic maturity analysis (Roa et al. 1999). In the case of the gummy shark this inaccuracy led to the 2PLF-maturity method performing comparably or better than the 3PLF methods in minimizing bias in \(R_0\) (Figure S11). Relatively wide confidence intervals were also obtained for \(P_{Max}\) in the empirical analysis for sandbar sharks, even with a total sample size of \textgreater{} 1000 females, 206 of which were in maternal condition. A similar sample size was used by Colonello \emph{et al}. (2016) to estimate plausible values of \(P_{Max}\) and maternity parameters for south Atlantic spiny dogfish.

@@

This unexpected result may be related to the gradual attainment of asymptotic maternal status. Maturity in sandbar sharks appears to occur over an extended size range. \(L_{5}\) and \(L_{95}\) are 146cm and 176cm -- a length interval that corresponds to around seven years given the sandbar shark's slow growth rate (Hale and Baremore 2013). With females maturing over a broad range of sizes and ages, it is possible that smaller females reproduce less frequently, while larger sharks may ultimately be capable of reproducing biennially. Given that few females appear to attain this size (Hale and Baremore 2013), the modal reproductive frequency is still likely at least triennial within the population. Further work would be required to confirm this hypothesis, however, such an outcome would have important implications for management; not only are larger females more fecund (Baremore and Hale 2012), they also reproduce more frequently. This implies that size selective fishing or the removal of larger and older female sharks could have a disproportionately greater impact on population productivity.

@@

Estimation of \(P_{Max}\) using the 3PLF-estimated method may also be a means to resolving the longstanding question of reproductive frequency in some rare and threatened chondrichthyans. White sharks, \emph{Carcharodon carcharias}, and whale shark, \emph{Rhincodon typus}, are two examples of intensively studied species where only fragmentary observations of female reproductive biology exist (Joung et al. 1996, Sato et al. 2016). In both species lack of data on reproductive frequency is a major impediment to population modelling and the development of management strategies (Huveneers et al. 2018, Bowlby and Gibson 2020). With many of these populations the focus of ongoing monitoring, non-lethal methods for assessing maternal state may eventually provide a way of collecting sufficient data for estimation of \(P_{Max}\) (Sulikowski et al. 2016).

@@

\bibitem[\citeproctext]{ref-natanson_presence_2019}
Natanson, L.J., Deacy, B.M., Joyce, W., and Sulikowski, J. 2019. Presence of a resting population of female porbeagles (\emph{{Lamna} nasus}), indicating a biennial reproductive cycle, in the western {North} {Atlantic} {Ocean}. Fish. B-noaa. \textbf{117}.

### 2024-06-23 rmds/manuscript.Rmd
changes

Walker [-@walker_reproduction_2005] recognised the need for a maternity function, as distinct from a maturity function, to accurately quantify reproductive capacity in chondrichthyans. For this purpose he used a non-linear, three-parameter logistic function (3PLF) of the form: $$Y_i \sim B(x_i; n_i, P_i)$$ $$E[Y_i] = n_iP_i = \frac{\alpha}{1 + e^{-(b_0 + b_1x_i)}}$$ where the proportion of individuals in a given length or age category, $x_i$, that are in maternal condition, $Y_i$, is a binomially distributed random variable, with an expected value equal to the probability of an individual from that category being in maternal condition, $P_i$, multiplied by the total number of individuals in the category, $n_i$. If $x$ is a continuous rather than categorical variable (i.e. $n = 1$), $Y_i$ reduces to a Bernoulli random variable [@zuur_analyzing_2007]. $\alpha$ is the upper asymptote of the curve, controlling the maximum value of $Y$ as $x$ approaches infinity. The lesser-used 3PLF reduces to the ubiquitous 2PLF when $\alpha = 1$, as is appropriate for most teleost and chondrichthyan populations if modeling maturity [@roa_estimation_1999; @quinn_quantitative_1999]. When $\alpha = 1$, the function also belongs to the class of generalised linear models; logistic transformation of the dependent variable allows $Y$ to be modeled as a linear function of $x_i$, where $b_0$ and $b_1$ are the intercept and slope, respectively [@zuur_analyzing_2007]. Alternatively, the model can be expressed in more biologically relevant terms as: $$E[Y_i] = P_{Max} \left ( 1 + e^{-ln(19)\left ( \frac{x_i - x_{50}}{x_{95} - x_{50}} \right )}  \right )^{-1} $$ where $x_{50}$ and $x_{95}$ are the sizes or ages at which 50% and 95% of the maximum proportion of individuals ($P_{Max}$) are in maternal condition. Instead of being fit to data on female maturity condition the model is fit to dichotomous data on female maternal condition (non maternal / maternal).

@@

$$
\hat{C}_{l} = \sum_a(F_{l}/Z_{l})(1-\exp(-Z_{l}))N_{l,a}
$$

@@

When using the 3PLF methods model performance typically declined as the periodicity of the reproductive cycle increased. This is seen in the positive correlation between $\hat{L'_{50}}$ and $\hat{P_{Max}}$, whereby true underlying $P_{Max}$ affected the magnitude and direction of bias in these parameters (Figure 2). With lower values of $P_{Max}$ it appeared to be more difficult for the model to separate the point of inflection in the logistic model and the upper asymptote. As true underlying $P_{Max}$ decreased there was also a greater potential for positive bias in $\hat{P_{Max}}$. Additionally, longer reproductive cycles resulted in fewer females in maternal condition, which was associated with larger bias (Figure 2).

@@

While the 3PLF-fixed method was in some cases able to reduce bias at lower sample sizes, a trade off in the use of this method was poorer interval coverage (Figure 4, Figure S6). For most simulations, interval coverage for $\hat{L'_{50}}$ was well below the expected level of 50%, irrespective of sample size. In contrast, for the 3PLF-estimated method interval coverage oscillated around 50% for both $\hat{L'_{50}}$ and $\hat{P_{Max}}$.

@@

Maternal data were re-analysed for `r nrow(plumbeus)` sandbar sharks including `r length(which(plumbeus$y == 1))` mature individuals of which `r round(100 * (length(which(plumbeus$z == 1)) / length(which(plumbeus$y == 1))))`% were in maternal condition. Using the 3PLF-estimated method, the maximum likelihood estimate for $\hat{P_{Max}}$ was 0.48 (Table 2). Despite having a sample size of \> 600 mature females, the proportion of maternal individuals at length was still uncertain and $\hat{P_{Max}}$ was estimated to lie between 0.39 and 0.60 with 95% confidence (Figure 7). For 3PLF-fixed models a value of $P_{Max} = 0.5$ was strongly supported ($\Delta_{AIC}$ = 14.15) over the alternative fixed value of $P_{Max} = 0.33$. The model with $P_{Max} = 0.5$ also outperformed the 3PLF-estimated method ($\Delta_{AIC}$ = 1.86). Given the fixed model had one fewer estimated parameter, both models had essentially the same level of support given the data [@burnham_model_2002].

@@

The empirical analysis carried out using data for the sandbar shark illustrates how novel insights can be gained from maternal data by estimating $P_{Max}$. Detailed reproductive studies of the western North Atlantic population by Baremore and Hale [-@baremore_reproduction_2012] and Piercy et al. [-@piercy_histological_2016] were ambiguous about the frequency of reproduction. In both studies, the low proportion of pregnant females and bimodality in ovarian follicle size led the authors to conclude that the reproductive cycle was most commonly triennial or possibly longer at the population level. Reanalysis of these combined data sets using the 3PLF-estimated method, however, resulted in a maximum likelihood estimate of $\hat{P_{Max}} = 0.48$, considerably larger than 0.37 - the proportion of pregnant mature females observed by Baremore and Hale [-@baremore_reproduction_2012]. Similarly, based on AIC values, a fixed value of $P_{Max} = 0.5$ had a much higher relative plausibility than a value of 0.33 (Table 2).

>>>>

Walker [-@walker_reproduction_2005] recognised the need for a maternity function, as distinct from a maturity function, to accurately quantify reproductive capacity in chondrichthyans. For this purpose he used a non-linear, three-parameter logistic function (3PLF) of the form: $$Y_i \sim B(x_i; n_i, P_i)$$ $$E[Y_i] = n_iP_i = \frac{\alpha}{1 + e^{-(b_0 + b_1x_i)}}$$ where the proportion of individuals in a given length or age category, $x_i$, that are in maternal condition, $Y_i$, is a binomially distributed random variable, with an expected value equal to the probability of an individual from that category being in maternal condition, $P_i$, multiplied by the total number of individuals in the category, $n_i$. If $x$ is a continuous rather than categorical variable (i.e. $n = 1$), $Y_i$ reduces to a Bernoulli random variable [@zuur_analyzing_2007]. The upper asymptote of the curve, $\alpha$, controls the maximum value of $Y$ as $x$ approaches infinity. The lesser-used 3PLF reduces to the ubiquitous 2PLF when $\alpha = 1$, as is appropriate for most teleost and chondrichthyan populations if modeling maturity [@roa_estimation_1999; @quinn_quantitative_1999]. When $\alpha = 1$, the function also belongs to the class of generalised linear models; logistic transformation of the dependent variable allows $Y$ to be modeled as a linear function of $x_i$, where $b_0$ and $b_1$ are the intercept and slope, respectively [@zuur_analyzing_2007]. Alternatively, the model can be expressed in more biologically relevant terms as: $$E[Y_i] = P_{Max} \left ( 1 + e^{-ln(19)\left ( \frac{x_i - x_{50}}{x_{95} - x_{50}} \right )}  \right )^{-1} $$ where $x_{50}$ and $x_{95}$ are the sizes or ages at which 50% and 95% of the maximum proportion of individuals ($P_{Max}$) are in maternal condition. Instead of being fit to data on female maturity condition the model is fit to dichotomous data on female maternal condition (non maternal / maternal).

@@

$$
C_{l} = \sum_a(F_{l}/Z_{l})(1-\exp(-Z_{l}))N_{l,a}
$$

@@

When using the 3PLF methods model performance typically declined as the periodicity of the reproductive cycle increased. This is seen in the positive correlation between $\widehat{L'_{50}}$ and $\widehat{P_{Max}}$, whereby true underlying $P_{Max}$ affected the magnitude and direction of bias in these parameters (Figure 2). With lower values of $P_{Max}$ it appeared to be more difficult for the model to separate the point of inflection in the logistic model and the upper asymptote. As true underlying $P_{Max}$ decreased there was also a greater potential for positive bias in $\widehat{P_{Max}}$. Additionally, longer reproductive cycles resulted in fewer females in maternal condition, which was associated with larger bias (Figure 2).

@@

While the 3PLF-fixed method was in some cases able to reduce bias at lower sample sizes, a trade off in the use of this method was poorer interval coverage (Figure 4, Figure S6). For most simulations, interval coverage for $\widehat{L'_{50}}$ was well below the expected level of 50%, irrespective of sample size. In contrast, for the 3PLF-estimated method interval coverage oscillated around 50% for both $\widehat{L'_{50}}$ and $\widehat{P_{Max}}$.

@@

Maternal data were re-analysed for `r nrow(plumbeus)` sandbar sharks including `r length(which(plumbeus$y == 1))` mature individuals of which `r round(100 * (length(which(plumbeus$z == 1)) / length(which(plumbeus$y == 1))))`% were in maternal condition. Using the 3PLF-estimated method, the maximum likelihood estimate for $\widehat{P_{Max}}$ was 0.48 (Table 2). Despite having a sample size of \> 600 mature females, the proportion of maternal individuals at length was still uncertain and $\widehat{P_{Max}}$ was estimated to lie between 0.39 and 0.60 with 95% confidence (Figure 7). For 3PLF-fixed models a value of $P_{Max} = 0.5$ was strongly supported ($\Delta_{AIC}$ = 14.15) over the alternative fixed value of $P_{Max} = 0.33$. The model with $P_{Max} = 0.5$ also outperformed the 3PLF-estimated method ($\Delta_{AIC}$ = 1.86). Given the fixed model had one fewer estimated parameter, both models had essentially the same level of support given the data [@burnham_model_2002].

@@

The empirical analysis carried out using data for the sandbar shark illustrates how novel insights can be gained from maternal data by estimating $P_{Max}$. Detailed reproductive studies of the western North Atlantic population by Baremore and Hale [-@baremore_reproduction_2012] and Piercy et al. [-@piercy_histological_2016] were ambiguous about the frequency of reproduction. In both studies, the low proportion of pregnant females and bimodality in ovarian follicle size led the authors to conclude that the reproductive cycle was most commonly triennial or possibly longer at the population level. Reanalysis of these combined data sets using the 3PLF-estimated method, however, resulted in a maximum likelihood estimate of $\widehat{P_{Max}} = 0.48$, considerably larger than 0.37 - the proportion of pregnant mature females observed by Baremore and Hale [-@baremore_reproduction_2012]. Similarly, based on AIC values, a fixed value of $P_{Max} = 0.5$ had a much higher relative plausibility than a value of 0.33 (Table 2).

### 2024-06-23 rmds/tables.Rmd
changes

---
output: 
  pdf_document:
    latex_engine: "pdflatex"
geometry: 
    - bottom=1.5cm
    - top=1.5cm
    - left=1.5cm
    - right=1.5cm
header-includes:
    - \fontsize{8}{20}
    - \usepackage{lscape}
    - \pagenumbering{gobble} 
tables: true
---

>>>>

---
output: 
  pdf_document:
    keep_tex: true
    latex_engine: "pdflatex"
geometry: 
    - bottom=1.5cm
    - top=1.5cm
    - left=1.5cm
    - right=1.5cm
header-includes:
    - \fontsize{8}{20}
    - \usepackage{lscape}
    - \pagenumbering{gobble} 
tables: true

---
